Understanding the impacts of video-guided activities on parent-child interaction

### 2019-07-07 paper/cogsci2019/cogsci2019.Rmd
updated Exp2 analyses

Parents' child-directed speech was transcribed and processed according to the same procedure used in Experiment 1.

@@

# predict word types
types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
summary(types_mod) # NA
```

We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.7) = `r e2TTR["conditionexp","zval"]`, *p*=.01).
There was no significant effect of age, nor a significant interaction.
A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}

@@

ms_lex <- d %>% group_by(Condition) %>%
  tidyboot_mean(MTLD) 
mltd_mean <- d %>% group_by(Condition)%>%
  summarise(mean = mean(MTLD), sd=sd(MTLD))

@@

multiplot(e2ttr, e2mtld, cols=2)
```

```{r e2token-type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
ms_tok <- d %>% group_by(Condition) %>%
  tidyboot_mean(tokens)

@@

@@

multiplot(e2tokens, e2types, cols=2)
```
```{r, e2-effect-size, echo=F}
ttr_means <- d %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means)
```

### Joint Attention
```{r, e2ja-regressions, echo=F, include=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
summary(d)
# triplicate variables: gender.x/y, ethnicity, english, num_lang, parent_ed, Exclude
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
e2ja = d
e2ja$age = scale(e2ja$age)

# did preregistration include this?
t.test(subset(e2ja, Condition=="Control")$bids, subset(e2ja, Condition=="Video")$bids)

# Total number of bids
bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja)
summary(bids_mod) # singular fit, covergence code: 0 - no effects
bmodMTLD <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
summary(bmodMTLD) # significant effect of condition! mean=3.2, 95%CI = [1.2, 5.2]

# Episodes of coordinated joint attention
cja_mod <- lmer(cja ~ age * condition + (1 | video), data = e2ja)
summary(cja_mod) # marginal condition: t(79) = 1.88 beta=-5.85 p=.06, age*condition beta=4.92 t(79) = 2.35 p=.02
# also singular fit, covergence code: 0

# Episodes of passive joint attention.
pja_mod <- lmer(pja ~ age * condition + (1 | video), data = e2ja)
summary(pja_mod) # age beta=-2.32 t(26.6) = 2.23 p<.05

# Total duration of passive joint attention.
pja_time_mod <- lmer(pja_length ~ age * condition + (1 | video), data = e2ja)
summary(pja_time_mod) # age beta=-15512 t(79) = 2.40 p<.05

# Total duration of coordinated joint attention.
cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
summary(cja_time_mod) # marginal age: beta=31757 t(79) = 1.81 p=.07
```

As specified in our preregistration, we fit five mixed-effects linear regressions predicting the following JA variables: parental bids, the number of episodes of coordinated JA and passive JA, and the total duration of coordinated and passive JA.
These JA variables were predicted as a function of fixed effects of condition, age (scaled and 0-centered), and gender, with random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(40.3) = `r e1bids["ConditionVideo","zval"]`, *p*<.01). 
There were no other significant effects.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
Figure X shows ... by condition.

@@

ms_bids <- d %>% group_by(Condition) %>%
  tidyboot_mean(bids)

e2bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=bids), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

e2tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

>>>>

Parents' child-directed speech was transcribed and processed according to the same procedure used in Experiment 1, and the preregistered regressions predicting TTR and number of tokens were carried out.

@@

# predict word types (NOT A PREREGISTERED REGRESSION)
#types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
#summary(types_mod) # NA
```

We fit a mixed-effects linear regression predicting TTR as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.7) = `r e2TTR["conditionexp","zval"]`, *p*=.01).
There was no significant effect of age, nor a significant interaction.
The preregistered regression of 
An exploratory similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2."}

@@

ms_lex <- d %>% group_by(Condition) %>%
  tidyboot_mean(MTLD)

@@

ms_tok <- d %>% group_by(Condition) %>%
  tidyboot_mean(tokens)

@@

multiplot(e2ttr, e2mtld, e2tokens, cols=3)
```

```{r e2token-type, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}

@@

#multiplot(e2tokens, e2types, cols=2)
```
```{r, e2-effect-size, echo=F}
ttr_means <- d %>% group_by(Condition) %>%
  summarise(mean = mean(TTR), sd = sd(TTR))
cohens_d(ttr_means)
```

### Joint Attention
```{r, e2ja-regressions, echo=F, include=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
summary(d)
# triplicate variables: gender.x/y, ethnicity, english, num_lang, parent_ed, Exclude
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
e2ja = d
e2ja$age = as.numeric(langcog::scale(e2ja$age, scale=FALSE)) # 0-centered but NOT scaled -- change text

# Total number of bids
bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja)
summary(bids_mod) # singular fit, convergence code: 0
e2bids <- get_lmer_reporting_values(bids_mod)
# Condition est = 3.25 t(79) = 3.65 p<.001
bids_bmod <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
summary(bids_bmod) # significant effect of condition! mean=3.2, 95%CI = [1.2, 5.2]

tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja)
summary(tja_mod) # singular fit, convergence code: 0
#                    Estimate Std. Error      df t value  Pr(>|t|) 
# age                 -4.6051     1.3927 79.0000  -3.306  0.00142 ** 
# ConditionVideo       1.5253     0.5626 79.0000   2.711  0.00822 ** 
# age:ConditionVideo   5.5193     2.1893 79.0000   2.521  0.01371 *

tja_bmod <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
summary(tja_bmod) # age n.s., sig effect of condition: mean=3.2 95%CI = [1.1, 5.2]
#                                        mean    sd     2.5%   25%    50%    75%    97.5%
# (Intercept)                             7.3    0.5    6.3    6.9    7.2    7.6    8.2 
# age                                    -4.3    1.5   -7.2   -5.3   -4.3   -3.3   -1.3 
# ConditionVideo                          1.5    0.7    0.2    1.1    1.5    1.9    2.9

# EXPLORATORY ANALYSES (NOT PREREGISTERED)

# Episodes of coordinated joint attention
cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja)
summary(cja_mod) #  Condition: t(79) = 2.47 beta=1.33 p=.02; age*Condition beta=4.92 t(79) = 2.35 p=.02
# also singular fit, convergence code: 0 - check Bayesian regression
cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
#                                        mean    sd     2.5%   25%    50%    75%    97.5%
# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6

# Episodes of passive joint attention.
pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
summary(pja_mod) # age beta=-2.32 t(26.6) = 2.23 p<.05

# Total duration of passive joint attention.
pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja)
summary(pja_time_mod) # singular - convergence code: 0, age beta=-15512 t(79) = 2.40 p<.05
pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
summary(pjat_bmod)
#                                        mean       sd         2.5%       25%        50%        75%        97.5%   
#(Intercept)                             11247.4     2193.1     6977.7     9822.1    11239.1    12655.2    15736.7
#age                                    -13924.2     7097.9   -27467.6   -18661.5   -14163.6    -9341.5      722.4
#ConditionVideo                            824.8     3098.5    -5399.6    -1190.0      846.8     2877.5     6867.3
#age:ConditionVideo                        108.3    11738.0   -23881.5    -7171.3      411.3     7778.3    22058.5

# Total duration of coordinated joint attention.
cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=31757 t(79) = 1.81 p=.07
cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
summary(cjat_bmod)
#                                           mean        sd          2.5%        25%         50%         75%      
#(Intercept)                              73053.4      5611.1     62252.3     69338.3     73049.6     76773.7
#age                                      28879.1     19079.4     -8533.5     16385.2     29112.3     41487.9
#ConditionVideo                            5745.4      7874.5     -9994.6       535.3      5725.3     11163.4
#age:ConditionVideo                       45792.3     30918.9    -14154.8     25281.7     45101.1     66074.2

e2_bids <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(bids)
e2_tja <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(total_ja) 
```

As specified in our preregistration, we fit five mixed-effects linear regressions predicting the following JA variables: parental bids, the number of episodes of coordinated JA and passive JA, and the total duration of coordinated and passive JA.
These JA variables were predicted as a function of fixed effects of condition, age (0-centered), with random intercepts per video.
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`) than in the Control condition (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(79) = `r e2bids["ConditionVideo","zval"]`, *p*<.001). 
There were no other significant effects.
There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.

Figure \ref{fig:e2ja} shows the mean number of bids and episodes of JA by condition.

@@

e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=bids), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Bids for Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

# total JA episodes
e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.3, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")
